Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-25 prop_iop.tex
prop_iop.tex \section{Cryptodeterminism} Updating...

Although a real or interval-valued probability measure could be used
to model whether we believe an event will happen or not, the classical
world could be model in an simpler way. If the complete initial condition
for tossing a coin or throwing a needle is known, we can determine
whether an event will happen or not for sure~\cite{DiaconisHolmesMontgomery2007}.
In another word, Newtonian physics could be modeled by a cryptodeterministic
measure defined as follow.

>>>>

\footnote{\yutsung{The word ''cryptodeterminism'' is used by Peres~\cite{peres1995quantum}
without a clear definition. I tried to check its meaning from other
sources. In~\cite{Atmanspacher2014}, Atmanspacher defined `one
might paraphrase the deterministic yet non-determinable behavior of
such systems as ``cryptodeterminism,''' where ``deterministic''
and ``determinable'' is defined in the same section as `The recent
creation of the term ``deterministic chaos'' expresses the tension
between ontic (hidden) lawfulness and epistemic (apparent) irregularity
in chaotic system. Our description of the underlying laws of nature,
e.g. by differential equations governing the dynamics of such systems,
is no doubt deterministic, but their observable behavior is everything
but determinable (in the sense of measurable, computable, or predictable)
with arbitrary precision.' Is Atmanspacher's usage consistent with
Peres' and ours here?}}Although a real or interval-valued probability measure could be used
to model whether we believe an event will happen or not, the classical
world could be model in an simpler way. If the complete initial condition
for tossing a coin or throwing a needle is known, we can determine
whether an event will happen or not for sure~\cite{DiaconisHolmesMontgomery2007}.
In another word, Newtonian physics could be modeled by a cryptodeterministic
measure defined as follow.
